Centralizers of higher enveloping algebras of Lie algebras

### 2020-08-10 draft.tex
og getting confused

See section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} 
for a brief discussion about centralizers to maps of $E_n$ algebras.

@@

Existing work provides insight into and context for the situation:
\begin{itemize}
\item Lurie and Francis give a characterization of the centralizer of any map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra $\tt{U}_n \fg = \cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
Our approach leverages these results as follows to prove the theorem.
\begin{enumerate}
\item First, we transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant. Lurie \cite{LurieHA} explains why we can work with the homotopy coherent version of prefactorization algebras, and then strictification theorems from the model category literature on operads say we can work with strict prefactorization algebras.
\item  In particular, given an $E_n$ algebra $B$,  let $\tt{B}$ denote a strict prefactorization algebra modeling~$B$.
Strictification lets us associate to the map $f: \UU_n \fg \to B$, a map $\tt{f}: \tt{U}_n \fg \to \tt{B}$ of strict prefactorization algebras. 
\owen{It might be better to first use the adjunction to get a map of homotopy-coherent Lie algebras $\fg \to B$ but \dots}
\item From the map $\tt{f}$, we read off an $\fg$-action on $\tt{B}$ intertwining with the structure maps of $\tt{B}$. 
That is, we have a prefactorization algebra $\tt{B}_f$ taking values in the 1-category of chain complexes of $\fg$-representations.
\item We then construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map
\[
\clies(\Omega \otimes \fg, \tt{B}_f) \otimes \tt{U}_n \fg \to \tt{B}_f
\]
such that precomposing with the map $1 \otimes \id_{\tt{U}_n \fg}$ is the map~$\tt{f}$.
Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, B_f) \to \tt{Z}_f$ as strict prefactorization algebras. 
\item We then verify that this map is a quasi-isomorphism on disks. 
\end{enumerate}
Hence it induces a weak equivalence of the associated $E_n$ algebras.

@@

\subsection{Recollections on $E_n$ algebras and prefactorization algebras}

\owen{Recall Jacob's results and what it means in conjunction with strictification}

\subsection{Enveloping $E_n$ algebras of Lie algebras}

@@

The second part of this result leads to the explicit models in our theorems.
Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.

\begin{rmk}
 It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to 
 $\Sigma^{n-1}B = B[n-1]$. Henceforth in this paper, we will simply use the notation  $B[n-1]$ for $\oblv_n(B)$, that is tacitly assume 
 $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
\end{rmk}

@@

We now use these results to prove the central claim of Theorem~\ref{thm: centralizer}.

>>>>

See section~\ref{sec: en background} for a brief discussion of $E_n$ algebras and their relationship with locally constant factorization algebras on $\RR^n$, section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} 
for a brief discussion about centralizers to maps of $E_n$ algebras.

@@

Existing work provides insight into and context for the situation:
\begin{itemize}
\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra ${\tt U}_n \fg = \cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
Our approach leverages these results as follows to prove the theorem.
\begin{enumerate}
\item First, we transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant. Lurie \cite{LurieHA} explains why we can work with the homotopy coherent version of prefactorization algebras, and then strictification theorems from the model category literature on operads say we can work with strict prefactorization algebras.
\item  In particular, given an $E_n$ algebra $B$,  let ${\tt B}$ denote a strict prefactorization algebra modeling~$B$.
Strictification lets us associate to the map $f: \UU_n \fg \to B$, a map ${\tt f}: {\tt U}_n \fg \to {\tt B}$ of strict prefactorization algebras. 
\owen{It might be better to first use the adjunction to get a map of homotopy-coherent Lie algebras $\fg \to B$ but I'm not sure this plays nicely with the other strictification\dots}
\item From the map ${\tt f}$, we read off an $\fg$-action on ${\tt B}$ intertwining with the structure maps of ${\tt B}$. 
That is, we have a prefactorization algebra ${\tt B}_f$ taking values in the 1-category $\Ch(\Rep(\fg))$ of chain complexes of $\fg$-representations.
\item We then construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map
\[
\clies(\Omega \otimes \fg, {\tt B}_f) \otimes {\tt U}_n \fg \to {\tt B}_f
\]
such that precomposing with the map $1 \otimes \id_{{\tt U}_n \fg}$ is the map~${\tt f}$.
Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, {\tt B}_f) \to {\tt Z}_f$ as strict prefactorization algebras. 
\item We then verify that this map is a quasi-isomorphism on disks. 
\end{enumerate}
Hence it induces a weak equivalence of the associated $E_n$ algebras.

@@

\subsection{Recollections on $E_n$ algebras and prefactorization algebras}
\label{sec: en background}

\owen{Recall Jacob's results and what it means in conjunction with strictification.}

\owen{I want to work with the colored operad of round disks (or rectilinear boxes) in $\RR^n$.}

Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.

\subsection{Enveloping $E_n$ algebras of Lie algebras}
\label{sec: enveloping}

@@

The second part of this result leads to the explicit models in our theorems.

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
Depending on one's preferences, one can work with an an $L_\infty$-algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
\end{rmk}

\owen{\label{note on little model} Note that if we work with the colored operad of disks/boxes, then Poincar\'e lemma tells us that we can use the strict model $\cliel(\fg[-n])$ rather than the fatter model $\cliels(\Omega^*_c(U) \otimes \fg)$. I think Ben actually shows this too. This would be worth explaining because we can then use a much simpler strictification of $f$.}

@@

We now turn to proving Theorem~\ref{thm: centralizer}.

\section{Strictifying the map $f: \UU_n \fg \to B$}

As a first step, we analyze the strictification of the map $f: \UU_n \fg \to B$ and show how it lets us view $B$ as an $E_n$ algebra in~$\Ch(\Rep(\fg))$.

By using the small model \owen{see my comment \ref{note on little model}}, we can strictify to obtain a map
\[
{\tt f}: \cliel(\fg[-n]) \to {\tt B}.
\]

\owen{And now I'm really confused.}

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to $\Sigma^{n-1}B = B[n-1]$. 
Henceforth in this paper, we will simply use the notation $B[n-1]$ for $\oblv_n(B)$, 
that is tacitly assume we $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
\end{rmk}
